---
title: "Module 4 synchronous class code (for class)"
output:
  pdf_document: default
  html_notebook: default
---

Video code and additional template code can be found in the ['Big Doc of Sample Code'](https://jupyter.utoronto.ca/hub/user-redirect/git-pull?repo=https%3A%2F%2Fgithub.com%2FUofT-sta130%2FSTA130-F21-module-4-extras&urlpath=rstudio%2F&branch=master). Use that link to pull the file in, it will be called STA130-F21-module-4-extras.

In this code demo, we are going to work through a test for one proportion.

## 1. State your hypotheses


## 2. Calculate your test statistic (real world)

### 2A. Load `tidyverse` and data

```{r, message=FALSE}
library(tidyverse)
```

### 2B. Save an object that says how many observations are in our sample data

```{r}

```

### 2C. Calculate the test statistic


```{r}

```

## 3. Simulate under the null hypothesis

### 3A. Set values for simulation


```{r}

```

### 3B. Automate simulation with a `for` loop (simulation world)

```{r}

```

### 3C. Turn results into a data frame so we can use ggplot for plotting

```{r}

```


## 4. Evaluate the evidence against the null hypothesis

```{r, eval=FALSE}
# the value from your null hypothesis
hypothesized_value <- ______

ggplot(sim_tibble, aes(x = simulated_statistics)) + 
  geom_histogram(bins = 30, colour = "black") +
  labs(x="Proportion of students picking C", y="Count", 
        title = "Simulated sampling distribution under the null hypothesis") +
  geom_vline(xintercept = hypothesized_value - abs(test_stat-hypothesized_value), 
             colour = "red") +
  geom_vline(xintercept = hypothesized_value + abs(test_stat-hypothesized_value), 
             colour = "blue") +
  theme_minimal() 
```


```{r}

```


## 5. Make a conclusion

### Strength of evidence conclusion


### What type of error are we at risk of making if we use a significance level of 0.1?


Some guidelines for how small is small? This table tells you how to comment on the **strength of evidence against** $H_0$.

| P-value                  | Evidence                           |
|--------------------------|------------------------------------|
| p-value \> 0.10          | no evidence against $H_0$          |
| 0.05 \< p-value \< 0.10  | weak evidence against $H_0$        |
| 0.01 \< p-value \< 0.05  | moderate evidence against $H_0$    |
| 0.001 \< p-value \< 0.01 | strong evidence against $H_0$      |
| p-value \< 0.001         | very strong evidence against $H_0$ |

